\textbf{\supplement}\vskip 2ex \mytitle\vskip 2ex

### 2023-05-31 paper-seb-supplementary-material.tex
Revisions getting closer to sending to Computer Journal, and renaming the repo

\iftrue
    \PassOptionsToPackage{hyphens}{url}
    \documentclass[10pt,a4paper]{article}
    \usepackage[text={6.5in,10in},centering]{geometry}    
    \usepackage{url}
    \usepackage{doi}
    \usepackage{longtable}
    \usepackage{color}
    \usepackage{amsmath,amssymb}
    \usepackage{fancyhdr}

    \usepackage{graphicx}
	\PassOptionsToPackage{dvipdfmx}{graphicx}

	\usepackage{amssymb}
	\usepackage{epstopdf}
    \def\httpURL#1{\href{http://#1}{\textcolor{blue}{#1}}}
    \def\LONGhttpURL#1#2{\href{http://#1}{\textcolor{blue}{#2}}}    
    \input paper-seb-macros.tex
\fi

\makeatletter
      \renewcommand{\thefootnote}{\arabic{footnote}}
      \let\oldbibcite=\bibcite
      % example: \bibcite{bad-code}{{31}{2020}{{Richards and Boudnik}}{{Richards and Boudnik}}}
      \newcount\mainNumberOfReferences \mainNumberOfReferences=0
      \def\bibcite#1#2{\global\advance\mainNumberOfReferences by 1\oldbibcite{#1}{#2}}
      \input paper-seb-main.aux 
      %\resetlinenumber[\MainPaperLastLine]
	  \let\bibcite=\oldbibcite
\makeatother

@@

\makeatletter

\def\rememberpage{\immediate\write\@auxout{\bslash gdef\bslash SupplementalLastPage{\thepage}}}

% putting \typeout in the right footer will get repeated warnings (which I hope will be noticed!)
% to complement the red text in the footer itself on every page
\@ifundefined{SupplementalLastPage}{\rfoot{\supplement\ \thepage\ \textcolor{red}{\bf(Rerun to get number of pages)}\typeout{* Rerun to get correct number of pages in the running footer}}}{\rfoot{\supplement\ \thepage/\SupplementalLastPage}}

\makeatother

\lfoot{\today}
\cfoot{}
\lhead{}
\rhead{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\thispagestyle{empty}

% this will be used to save cross references that can be used in the main paper too
\newwrite\infofileForMain
\immediate\openout\infofileForMain=generated/info-for-main.tex

@@

\def\dotalph#1{\ifnum\csname c@#1\endcsname>0 .\alph{#1}\fi}

%\makeatletter
%\def\globalLabel#1{% we also need journal code-policies to be used in the main paper...
%\typeout{Global globalLabel: #1}%
%\immediate\write\infofileForMain{\bslash newlabel{#1}{{\arabic{section}}{\thepage}{DUMMYA}{DUMMYB}{DUMMYC}}}
%% as well as in the current document....
%\immediate\write\@auxout{\bslash newlabel{#1}{{\bslash arabic{section}\dotalph{subsection}}{\thepage}{AAA}{BBB}{CCC}}}
%}
%\def\globalTableLabel#1{% we also need journal code-policies to be used in the main paper...
%\typeout{Global globalTableLabel: #1}%
%\immediate\write\infofileForMain{\bslash newlabel{#1}{{\arabic{table}}{\thepage}{DUMMYA}{DUMMYB}{DUMMYC}}}
%% as well as in the current document....
%\immediate\write\@auxout{\bslash newlabel{#1}{{\bslash arabic{table}\dotalph{subsection}}{\thepage}{AAA}{BBB}{CCC}}}
%}
%\def\globalLabelValue#1#2{% we also need journal code-policies to be used in the main paper...
%\typeout{Global globalLabelValue: #1 := #2}%
%\immediate\write\infofileForMain{\bslash newlabel{#1}{{#2}{\thepage}{AAA}{BBB}{CCC}}}
%}
%\makeatother

@@

\item Ethics Boards also have to deal with software, and it is clear that they often fail to do this effectively. The case of the retraction of a peer reviewed articles for \emph{The Lancet\/} \cite{science-lancet1,science-lancet2,lancet-learning} and the \emph{Journal of Vascular Surgery\/} \cite{jvs1,jvs2,jvs3}, discussed in the main paper, are cases in point.
\end{itemize}

@@

If version control is not used, one has no idea what the current program actually is. {Version control is essential for \emph{reproducibility\/}: \cite{basic-reproducibilty,reproducibility} it enables efforts to duplicate work to start with the exact version that was used in any published paper, provided that the published paper discloses the version and a URL for the relevant repository. Note that version control should also be used for data and web site data used by code, otherwise the results reported are not replicable.}

@@

Computers themselves are also a part of the problem. Na\"\i vely modifying a program (as may occur during debugging) typically makes it more complex, more \emph{ad hoc}, and less scrutable. Programs can be written so that it is not possible to determine what they do or how they do it (whether by deliberate obfuscation, as in malware, or accidentally), except by running them, if indeed it is possible to exactly reproduce the necessary context to do so \cite{framework}. The point is, introducing bugs should be avoided so far as possible in the first place, and programs should routinely have assertions and other methods to detect those bugs that are introduced (see this paper's \supplement\ for more discussion of standard programming methodologies).

@@

{Significant cyber-vulnerabilities result from there being no difference between code and data. For example: an email arrives, which brings data to a user. The user opens an attachment, perhaps a word processor text document, which is more data. The word processor runs macros in the text document --- but now it is code. The macros move data onto the user's disc. The data there then runs as code, and corrupts the user's data across the disc --- which includes both data and code stored in files. And so on. Each step of a computer virus infection crosses over non-existent ``boundaries'' between data and code \cite{viruses}.}

@@

\immediate\write\infofileForMain{\bslash def\bslash MaxMainPaperCitationNumber{\the\temporary}}

@@

\def\maprepo#1{\immediate\write\infofileForSupplement{\bslash expandafter\bslash def \bslash csname cite-#1\bslash endcsname{[\the\bibciten]}}}

@@

\immediate\closeout\infofileForMain
\immediate\closeout\infofileForSupplement
\rememberpage
\end{document}

>>>>

\documentclass[10pt,a4paper]{article}
\usepackage[text={6.5in,10in},centering]{geometry}    
\usepackage{url}
\PassOptionsToPackage{hyphens}{url}
\usepackage{doi}
\usepackage{longtable}
\usepackage{color}
\usepackage{amsmath,amssymb}
\usepackage{fancyhdr}    
\usepackage{graphicx}
\PassOptionsToPackage{dvipdfmx}{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}

\def\httpURL#1{\href{http://#1}{\textcolor{blue}{#1}}}
\def\LONGhttpURL#1#2{\href{http://#1}{\textcolor{blue}{#2}}}    
\input paper-seb-macros.tex

\makeatletter
      \renewcommand{\thefootnote}{\arabic{footnote}}
      % count the number of bibcite{name}{value} in paper-seb-main.aux
      \let\oldbibcite=\bibcite
      \newcount\mainNumberOfReferences \mainNumberOfReferences=0
      \def\bibcite#1#2{\global\advance\mainNumberOfReferences by 1\oldbibcite{#1}{#2}}
      \input paper-seb-main.aux 
      \let\bibcite=\oldbibcite
\makeatother

@@

\rfoot{}
\lfoot{}
\cfoot{\thepage}
\lhead{\mytitle: \supplement}
\rhead{Harold Thimbleby}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\thispagestyle{empty}

@@

@@

\item Ethics Boards also have to deal with software, and it is clear that they often fail to do this effectively. The case of the retraction of a peer reviewed articles for \emph{The Lancet\/} \cite{science-lancet1,science-lancet2,lancet-learning} and the \emph{Journal of Vascular Surgery\/} \cite{jvs1,jvs2,jvs3}, discussed in section 
\ref{supplement-vascular-surgery-note}, are cases in point.
\end{itemize}

@@

If version control is not used, one has no idea what the current program actually is. {Version control is essential for \emph{reproducibility\/} \cite{basic-reproducibilty,reproducibility} (see also section \ref{reproducibility-concerns}): it enables efforts to duplicate work to start with the exact version that was used in any published paper, provided that the published paper discloses the version and a URL for the relevant repository. Note that version control should also be used for data and web site data used by code, otherwise the results reported are not replicable.}

@@

Computers themselves are also a part of the problem. Na\"\i vely modifying a program (as may occur during debugging) typically makes it more complex, more \emph{ad hoc}, and less scrutable. Programs can be written so that it is not possible to determine what they do or how they do it (whether by deliberate obfuscation, as in malware, or accidentally), except by running them, if indeed it is possible to exactly reproduce the necessary context to do so \cite{viruses}. The point is, introducing bugs should be avoided so far as possible in the first place, and programs should routinely have assertions and other methods to detect those bugs that are introduced (see this paper's \supplement\ for more discussion of standard programming methodologies).

@@

Significant cyber-vulnerabilities result from there being no difference between code and data. For example: an email arrives, which brings a paper to work on or other data to a user. The user opens the attachment, perhaps a word processor text document, which is more data. The word processor runs macros in the text document --- but now it is code. The macros move data onto the user's disk. The data there then runs as code, and corrupts the user's data across the disk --- which includes both data and code stored in files. And so on, spreading around the world when this user emails their work to a colleague. Each step of a computer virus infection crosses over non-existent ``boundaries'' between data and code \cite{viruses}.

@@

@@

\catcode`\%=11
\immediate\write\infofileForSupplement{% map Git repo names to their citation numbers}
\immediate\write\infofileForSupplement{% generated by paper-seb-supplementary-material.tex}
\catcode`\%=14
\def\maprepo#1{\immediate\write\infofileForSupplement{\bslash expandafter\bslash def \bslash csname cite-#1\bslash endcsname{[\the\bibciten]}}}

@@

\immediate\closeout\infofileForSupplement
\end{document}
